# b) Model interpretation

Let us load the dataset:
```{r}
filepath <- "https://www.math.ntnu.no/emner/TMA4315/2017h/mountains"
mount <- read.table(
	file = filepath,
	header = TRUE,
	col.names = c("height", "prominence", "fail", "success")
)
```

Now we fit a logit model to the data, using the height and prominence of the mountains as predictors.

```{r}
fit <- glm(
	cbind(success, fail) ~ height + prominence,
	data = mount,
	family = binomial(link = "logit")
)
summary(fit)
```

## Interpretation of the model parameters

We observe that the coefficients for both `height` _and_ `prominence` are negative. This means that the odds for a successful summit _decreases_ as the height/prominence _increases_, which makes sense.

In order to further analyze the model, it is easier to inspect the exponential transform of the coefficients.

```{r}
odds <- exp(fit$coefficients)
odds
```

If the chance of a successful summit of a given mountain has a predicted odds of $\Theta_{odds}$, then an identical mountain except for it being one unit taller (but not any more prominent), has a predicted odds of $`r odds["height"]` \cdot \Theta_{odds}$. Likewise for a change in prominence, but not height, the new predicted odds will be $`r odds["prominence"]` \cdot \Theta_{odds}$.

Here we have ignored the fact that height and prominence are inherently interlinked; changing one will often change the other.

The intercept gives us the odds for a successful summit of a completely flat mountain, $`r odds[1]`$. The model therefore predicts a mountaineer to trip every 90 thousand steps on average, which is not too unreasonable.
