## c) Poisson regression
We assume that each team has a single parameter measuring their strength, denoted $\beta_{A}$ for team A and so on, and that the number of goals scored by team A when playing team B is Poisson distributed with an logit-link. The intensity is assumed to be determined by the strength of team A, the strength of team B and the home advantage, which is assumed to be independent of which teams are playing. This means that if A is playing against team B, and team A is the home team, the number of goals scored by team A is assumed to be Poisson distributed with mean $\lambda$, where
$$\ln{\lambda} =\beta_0 + \beta_{home} + \beta_A - \beta_B.$$
The number of goals scored by team B will have intensity 
$$\ln{\lambda} =\beta_0 - \beta_A + \beta_B.$$

Each match contributes with two data points, the number of goals scored by the home team and the number of goals scored by the away team. These numbers are assumed to be independent, and thus we have $2 \cdot n(n-1) = 480$ responses. In order to do the regression, we construct a $480 \times 18$ design matrix `X` with the following coding: 

* $x_{home}$: 1 if the score is for a home team, and 0 if it is for an away team. 
* $x_A$: 1 if the score is for team A, -1 if team A is the opposing team and 0 otherwise.

```{r}
#Creating the design matrix
X = matrix(0,nrow=480,ncol=18)
colnames(X) = c("Intercept","Home",tippeliga$home[1:16])
for(i in 1:240){
  #Home:
  X[i,"Home"] = 1
  X[i,"Intercept"] = 1
  X[i,tippeliga$home[i]] = 1
  X[i,tippeliga$away[i]] = -1
  
  #Away:
  X[i+240,"Intercept"] = 1
  X[i+240,tippeliga$home[i]] = -1
  X[i+240,tippeliga$away[i]] = 1
}
X = X[,-3] #remove Aalesund
goals = c(tippeliga$yh,tippeliga$ya)
```

The column representing Aalesund is removed in order to give a unique solution. Hence, the strength parameter of Aalesund is included in the intercept. 

The maximum likelihood estimates of the betas is found solving $s(\hat \beta) = 0$ numerically using `optim` with `method = "BFGS"`. 
```{r,echo=FALSE}
myglm <- function(formula, data = list(), contrasts = NULL, ...){
  # Extract model matrix & responses
  mf <- model.frame(formula = formula, data = data)
  X  <- model.matrix(attr(mf, "terms"), data = mf, contrasts.arg = contrasts)
  y  <- model.response(mf)
  terms <- attr(mf, "terms")
  
  #The log-likelihood-function
  ML = function(x){
    MLE = 0
    for(i in 1:length(y)){MLE = MLE +y[i] * t(X[i,]) %*% x-exp(t(X[i,]) %*% x)}
    return(-1*MLE)
  }
  
  #Maximizing the log-likelihood
  MLE = optim(matrix(0,nrow=17,ncol=1),ML,method = "BFGS")
  betahat = MLE$par
  row.names(betahat) = c("Intercept","Home",tippeliga$home[2:16])
  colnames(betahat) = "Estimate"
  
  est <- list(terms = terms, model = mf)
  
  # Store call and formula used
  est$call <- match.call()
  est$formula <- formula
  est$coefficients <- betahat
  
  # Set class name. This is very important!
  class(est) <- 'myglm'
  
  # Return the object with all results
  return(est)
}
```
The ranked strenghts given by this method is
```{r}
strengths = myglm(goals ~ -1 + X)$coefficients
strengthsRank = strengths[3:17, , drop= FALSE]
strengthsRank = strengthsRank[order(-strengthsRank[,1]), ,drop=FALSE]
strengthsRank
```
Since we have set $\beta_{Aalesund}$ to zero, Aalesund lies between Lillestroem and Stabaek. 

Comparing to the ranking in point b), we see that the top three and the bottom team have the same ranking when ranking the estimated strength parameters. In between the teams have changed their positions. This is due to the ranking system in tippeligaen which does not necessarily ensure that a stronger team gets a higher ranking than e weaker team. For instance, a one goal victory gives the same amount of points as a five goal victory in the ranking system, while a five goal victory will boost the strength parameter of a team a lot more than a one goal victory. In the ranking system one goal can change the result of a match and give a team 3 points instead of 1 point. Thus, some goals are a lot more important to the rankings than others. When calculating the strength parameters all goals are equally important. 


The home advantage and intercept is
```{r}
strengths[1:2,1,drop=FALSE]
```
According to this model the home advantage is approximately equivalent to the strength difference between Rosenborg and Brann. 

