## c) Poisson regression
We assume that each team has a single parameter measuring their strength, denoted $\beta_{A}$ for team A and so on, and that the number of goals scored by team A when playing against team B is Poisson distributed with a logit-link. The intensity is assumed to be determined by the strength of team A, the strength of team B, and the home advantage, the latter is assumed to be independent of which teams are playing.
This means that if A is playing against team B, and team A is the home team, the number of goals scored by team A is assumed to be Poisson distributed with mean $\lambda$, where
$$\ln{\lambda} =\beta_0 + \beta_{\text{home}} + \beta_\text{A} - \beta_\text{B}.$$
The number of goals scored by team B will have logaritmic intensity 
$$\ln{\lambda} =\beta_0 - \beta_\text{A} + \beta_\text{B}.$$

Each match contributes two data points, the number of goals scored by the home team and the number of goals scored by the away team. These numbers are assumed to be independent, and thus we have $2n(n-1) = 480$ responses. In order to do the regression, we construct a $480 \times 18$ design matrix `X` with the following coding: 

* $x_{\text{home}}$: 1 if the score is for a home team, and 0 if it is for an away team. 
* $x_\text{A}$: 1 if the score is for team A, -1 if team A is the opposing team and 0 otherwise.

```{r}
#Creating the design matrix
X = matrix(0,nrow=480,ncol=18)
colnames(X) = c("Intercept","HomeAdvantage",tippeliga$home[1:16])
for(i in 1:240){
  #Home:
  X[i,"HomeAdvantage"] = 1
  X[i,"Intercept"] = 1
  X[i,tippeliga$home[i]] = 1
  X[i,tippeliga$away[i]] = -1
  
  #Away:
  X[i+240,"Intercept"] = 1
  X[i+240,tippeliga$home[i]] = -1
  X[i+240,tippeliga$away[i]] = 1
}
X = X[,-3] #remove Aalesund
goals = c(tippeliga$yh,tippeliga$ya)
```

The column representing Aalesund is removed in order to give a unique solution. Hence, the strength parameter of Aalesund is included in the intercept. 

The maximum likelihood estimates of the betas is found solving the score function $s(\hat \beta) = 0$ numerically using `optim` with `method = "BFGS"`. 
```{r,echo=FALSE}
myglm <- function(formula, data = list(), contrasts = NULL, ...){
  # Extract model matrix & responses
  mf <- model.frame(formula = formula, data = data)
  X  <- model.matrix(attr(mf, "terms"), data = mf, contrasts.arg = contrasts)
  y  <- model.response(mf)
  terms <- attr(mf, "terms")
  
  #The log-likelihood-function
  ML = function(x){
    MLE = 0
    for(i in 1:length(y)){MLE = MLE +y[i] * t(X[i,]) %*% x-exp(t(X[i,]) %*% x)}
    return(-1*MLE)
  }
  
  #Maximizing the log-likelihood
  MLE = optim(matrix(0,nrow=17,ncol=1),ML,method = "BFGS")
  betahat = MLE$par
  row.names(betahat) = c("Intercept","Home",tippeliga$home[2:16])
  colnames(betahat) = "Estimate"
  
  est <- list(terms = terms, model = mf)
  
  # Store call and formula used
  est$call <- match.call()
  est$formula <- formula
  est$coefficients <- betahat
  
  # Set class name. This is very important!
  class(est) <- 'myglm'
  
  # Return the object with all results
  return(est)
}
```
Since we have set $\beta_{\text{Aalesund}}$ to zero and removed it from the design matrix it must be added manually. The ranked strenghts given by this method is
```{r}
strengths = myglm(goals ~ -1 + X)$coefficients

#Removing Intercept and HomeAdvantage, keep row names
strengthsRank = strengths[3:17, , drop=FALSE]

#Adding Aalesund
Aalesund <- matrix(0,nrow=1,ncol=1)
row.names(Aalesund) = "Aalesund"
strengthsRank = rbind(strengthsRank,Aalesund)

#Sorting the strenght parameters, keep row names
strengthsRank = strengthsRank[order(-strengthsRank[,1]), ,drop=FALSE] 
strengthsRank
```

Compared to the ranking in task 2 b), we see that the top three and the bottom team have the same ranking when ordering based on the estimated strength parameters. This is not the case for the rest of the teams. This is due to the ranking system in tippeligaen which does not necessarily ensure that a stronger team gets a higher ranking than a weaker team. For instance, a one goal victory gives the same amount of points as a five goal victory in the ranking system, while a five goal victory will boost the strength parameter of a team a lot more than a one goal victory. In the ranking system one goal can change the result of a match and give a team 3 points instead of 1 point. Thus, some goals are a lot more important to the rankings than others. When calculating the strength parameters all goals are equally important. 


The home advantage and intercept is
```{r}
strengths[1:2,1,drop=FALSE]
```
According to this model the home advantage is approximately equivalent to the strength difference between Rosenborg and Brann. 

