## d) Simulation 
In order to investigate the variance in the expected results and find out if the winning team really was the bes we simulate 1000 seasons of tippeligaen based on the estimated parameters in point c). The results are displayed in a histogram, sorted based on their position in Tippeligaen 2016. 
```{r,echo=TRUE,display=FALSE,fig2, fig.height = 10, fig.width = 10, fig.align = "center"}
#Simulation
rankings = matrix(0,nrow=16,ncol=1000)
row.names(rankings) = row.names(ranking(tippeliga))

set.seed(1792)
betahat = myglm(goals ~ -1 + X)$coefficients
for(season in 1:1000){
  tippeligaSim = data.frame(
    tippeliga$home,
    tippeliga$away,
    matrix(0,nrow=240,ncol=1),
    matrix(0,nrow=240,ncol=1),
    stringsAsFactors=FALSE
  )
  colnames(tippeligaSim) = c("home","away","yh","ya")
  for(i in 1:240){
    tippeligaSim$yh[i] = rpois(1,lambda = exp(t(X[i,]) %*% betahat))
    tippeligaSim$ya[i] = rpois(1,lambda = exp(t(X[i+240,]) %*% betahat))
  }
  tippeligaSimScores = ranking(tippeligaSim)
  for(i in 1:16){
    rankings[row.names(tippeligaSimScores[i,1,drop=FALSE]),season] = i
  }
}

#Plot simulated results
g = ggplot(data = melt(rankings),aes(x = value,fill=as.factor(Var1))) + 
  facet_wrap( ~ as.factor(Var1),ncol=4,strip.position = "bottom") +
  guides(fill=FALSE) +
  geom_histogram(binwidth=1,center=0,col="white") +
  theme_fivethirtyeight() + 
  theme(panel.grid.minor.x  = element_blank(),panel.grid.major.x = element_blank()) + 
  theme(strip.text = element_text(size=16)) +
  scale_x_continuous(breaks=1:16,limits = c(0,17))
g
```

Here, Rosenborg has a win rate of 
```{r}
rate <- sum(rankings["Rosenborg",]==1)/1000
rate
```
This means that with the given strengths Rosenborg would win `r rate` % of the seasons, while Brann would win 5 % and Odd 1.6 %. Thus, we can safely conclude that Rosenborg is truly the best team. Start has a loss rate of 84.1 % and is clearly the weakest team. 

In the middle of the ranking there are few points distinguishing the teams and the distributions are very similar. According to this model there seems to be only coincidences, and nor team strength, determining where Sarpsborg_08 places between 4th place or 14th place, since the distribution is almost uniform. Fourth place would give qualification to Europa League, while 14th place could result in relegation. 

There are no teams that seems to have gotten position that is way off according to their distribution. However, Tromsø should probably have faced relegation rather than Bodø Glimt, and Molde seems to be at bit stronger than Haugesund and would maybe have done better in the Europe League. 

In the end football is not always about being the strongest team, but managing to pull in the victory when needed. Therefore, it does not matter much who was really the strongest when they did not manage to turn strength into points. It is however interesting to note that there is a lot of variance in the results, and apparently almost anything can happen.

